\section{Overview}
Starterkit is a document that is used to demonstrate how \skAutoDoc can be
used to setup a unit test, verification test, or a tool validation test
document.

An \skAutoDoc report consists of two distinct parts: 1) text and 2) a
program. Text describes requirements, test expectation, and test results, and
a program automates running Test Plans, Test Suites, and Test Steps that is
compliant with the \skOutputFactory specified by the \skAmber driver.

The goal of this report is to demonstrate how to specialize an \skAutoDoc for your
specific purposes.  This report does not hook into \skAmber.  \skAmber has
a similar report that describes the requirements for the \skInputFactory and
the \skOutputFactory.

Several sections in section 1 will seam out of place, and perhaps will read
award. I have included them so that you will see \skAutoDoc framework reuses
documentation parts.

\subsection{\skStarterkit}
The contents of \skStarterkit is listed below.  Page layout, headers, footers,
and table of contents is driven by the \LaTeX\ document class \skTlcArticle.

\begin{verbatim}
  \documentclass[10pt]{tlc-article}
  \begin{document}
    \tlcTitlePageAndTableOfContents
      {Autodoc \\ Starter Kit}
      {Gary A. Howard}This
      {This document demonstrates how-to use an automated documentation
      (\skAutoDoc) frameework.}

    \input{\toolTestDir/main.tex}
    \makeatletter
    \tlcDebug
    \autodocDebug

  \end{document}
\end{verbatim}

\subsection{\skToc}
\textbf{\skTlcArticle} provides the \skToc to provide the document title, table
of contents, author name, and document abstract that you read on the first page.

\subsection{additional-layout}
\skTlcArticle provides a hook to \skAdditionalLayout to allow you to specialize
your documents layout.  The primary contents of this documents
\skAdditionalLayout file is shown below.

\begin{verbatim}
  \def\autodocDir{..}
  \input{\autodocDir/boilerplate/project-directories.tex}
\end{verbatim}

\skAutoDocDir is the location on your file system of the \skAutoDoc repository.
\skProjectDirTex is an \skAutoDoc file that defines locations of files within
the \skAutoDoc folder.

\subsection{main}
All text found in \skBoilerplate is common to all \skAutoDoc documents.  Each
document consist of four major sections:

\begin{description}[leftmargin=3cm, style=nextline]
  \item[Overview:] This section provide an overview of the document.  It has
    been designed with quality and regulatory compliance in mind.  The goal is
    to assemble documents that a suitable for your Design History File, or may
    be used when submitting records to the Food and Drug Administration.

  \item[Requirements:] Identifies the requirements of the document.  This may be
    user needs, products requirements, or testing requirements.

  \item[Test Plan Overview:] This section will vary based on the type of testing
    that is being described.  This section will contain test evidence when
    combined with \skAmber.

  \item[Conclusion:] This section is the conclusion you write after you have
    reviewed your test evidence.  By default, \skAutoDoc, provides a default
    conclusion that you override by placing a file named \skConclusion in same
    directory as \skStarterkit.

\end{description}

\skAutoDoc provides three document templates.

\begin{description}[leftmargin=3cm, style=nextline]
  \item[\skToolTest:] This template was designed to standardize
    \skToolTestTemplate.

  \item[\skUnitTest:] This template can be used when your project requires
    \skUnitTestTemplate.

  \item[\skVerTest:] \skVerTestTemplate template is use do when you need to
    record \skUnitTestTemplate results.

\end{description}

The term Test has been abstracted to mean any test type including: unit test,
verification test, validation test, integration test and tool validation test.

\subsection{\skTlcDebug}
\skTlcDebug is a command provided by \skTlcArticle to assist you when you are
having difficulty with \LaTeX\ text expansion.  You will notice the final
sections of this document has debugging information.

\subsection{\skAutoDocDebug}
\skAutoDocDebug is similar to \skTlcDebug with a focus on debugging \skAutoDoc
documents.
