% {{{ Autodoc Overview 

\section{Autodoc Overview}

\todo[inline]{Complete section. This section has content that needs to move to
other sections.}%

The contents of \adStarterkit\ are listed below.  Page layout, headers, footers,
and table of contents is driven by the \LaTeX\ document class \adTlcArticle.

\begin{verbatim}
  \documentclass[10pt]{tlc-article}
  \begin{document}
    \tlcTitlePageAndTableOfContents
      {Autodoc \\ Starter Kit}
      {Jane Doe}
      {This document demonstrates how-to use (\adAutoDoc) a \LaTeX\
      documentation framework. \adAutoDoc declares this a tool-test document
      type.}

    \input{\toolTestDir/main.tex}

    \makeatletter
    \tlcDebug
    \autodocDebug
    \makeatother

  \end{document}
\end{verbatim}

\subsection{\adToc}
\textbf{\adTlcArticle} provides the \adToc\ to provide the document title, table
of contents, author name, and document abstract that you read on the first page.

\subsection{additional-layout}
\adTlcArticle\  provides a hook to \adAdditionalLayout\ to allow you to specialize
your documents layout.  The primary contents of this documents
\adAdditionalLayout\ file is shown below.

\begin{verbatim}
  \def\autodocDir{..}
  \input{\autodocDir/boilerplate/project-directories.tex}
\end{verbatim}

\adAutoDocDir\ is the location on your file system of the \adAutoDoc\ repository.
\adProjectDirTex\ is an \adAutoDoc\ file that defines locations of files within
the \adAutoDoc\ folder.

\subsection{main}
All text files found in \adBoilerplate\ are common to all \adAutoDoc\ documents.
Each document consist of four major sections:

\begin{description}[leftmargin=3cm, style=nextline]
  \item[Overview:] This section provide an overview of the document.  It has
    been designed with quality and regulatory compliance in mind.  The goal is
    to assemble documents that a suitable for your Design History File, or may
    be used when submitting records to the Food and Drug Administration.

  \item[Requirements:] Identifies the requirements of the document.  This may be
    user needs, products requirements, or testing requirements.

  \item[Test Plan Overview:] This section will vary based on the type of testing
    that is being described.  This section will contain test evidence when
    combined with \adAmber.

  \item[Conclusion:] This section is the conclusion you write after you have
    reviewed your test evidence.  By default, \adAutoDoc, provides a default
    conclusion that you override by placing a file named \adConclusion\ in same
    directory as \adStarterkit.

\end{description}

\adAutoDoc\ provides three document templates.

\begin{description}[leftmargin=3cm, style=nextline]
  \item[\adToolTest:] This template was designed to standardize
    \adToolTestTemplate.

  \item[\adUnitTest:] This template can be used when your project requires
    \adUnitTestTemplate.

  \item[\adVerTest:] \adVerTestTemplate\ template is use do when you need to
    record \adUnitTestTemplate\ results.

\end{description}

The term Test has been abstracted to mean any test type including: unit test,
verification test, validation test, integration test and tool validation test.

\subsection{\adTlcDebug}
\adTlcDebug\ is a command provided by \adTlcArticle\ to assist you when you are
having difficulty with \LaTeX\ text expansion.  You will notice the final
sections of this document has debugging information.

\subsection{\adAutoDocDebug}
\adAutoDocDebug\ is similar to \adTlcDebug\ with a focus on debugging \adAutoDoc\
documents.

% -------------------------------------------------------------------------- }}}
